Recognizing emotions with technology and starting discussions

### 2018-01-21 paper.tex
Add subquestions to introduction

>>>>

To answer the main question, several sub-questions have been formulated relevant to the main question. 
The prototype should be capable of helping us answering these questions by collecting relevant data. 
Throughout this paper, these sub-questions will be answered. For example, to answer the main question, 
we want to know if our prototype gives accurate predictions in which the participants can relate. 
We also want to know if participants are willing to start a discussion on their own, or if they need some 
other kind of incentive alongside the prototype. It's also very important to know if the discussion has the 
desired effect, which is making the content relevant.
